Parallel Tractability of Ontology\\ Materialization: Technique and Practice

### 2018-02-04 parallel-tractability-J-v9/evaluation.tex
small changes

\textbf{LUBM}. In the Semantic Web community, LUBM
(The Lehigh University Benchmark) is proposed to
facilitate the evaluation of ontology-based systems
in a standard and systematic way.
In the latest version of LUBM,\footnote{http://swat.cse.lehigh.edu/projects/lubm/}
the core ontology contains 48 classes and 32 properties, used to describe the departments and the staff of
universities. By setting a different number of universities for an ontology-generator, users can get datasets of any size based on the core ontology.
%
The statements about properties in the LUBM core ontology, such as inverse property statements,
can be rewritten into the datalog rules of the form (R1), (R2) and (R3) in Table~\ref{tab:dhl}.
Most of the statements about classes can be rewritten into the datalog rules of the form (T1) and (T3)
in Table~\ref{tab:dhl}. Five axioms have, however, the form $A\sqsubseteq\exists R.B$,
which requires existentially quantified variables in the rule head when rewriting
the axiom into a logic rule: $A(x)\rightarrow\exists y(R(x,y)\wedge B(y))$ ($\tau$),
where a free variable $y$ is introduced. This kind of axiom is a general case of (T4) in Table~\ref{tab:dhl}
for which $A$ is actually replaced by the top concept $\top$.
Similarly to how we handle (T4), we can also eliminate the free variable $y$
in rule $\tau$ via Skolemization, i.e., by replacing the variable $y$ with a new constant $o_R^{A,B}$.
In this way, rule $\tau$ can be rewritten into $A(x)\rightarrow R(x,o_R^{A,B})\wedge B(o_R^{A,B})$.
If we only focus on the materialization task, the rewriting approach via Skolemization guarantees the
completeness and correctness \cite{GrauHKKMMW13}.
On the other hand, rule $\tau$ is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
In summary, if the above kind of rule is not considered {\color{red}
  or rewriting is used},
the materialization of a LUBM dataset can be handled by
Algorithm~$\mathsf{A}_{\text{opt}}^{\psi}$. {\color{red}(Did you use
  rewriting or did you drop the axioms?)}

@@

According to the semantics given to YAGO \cite{SuchanekKW08}, the built-in properties in YAGO,
i.e., \texttt{domain, range, subClassOf, subRelationOf} and \texttt{type} act in the same
way as the terms in RDFS statements of the form (1--5) in Table~\ref{tab:rdfs}, respectively.
In contrast to RDFS, YAGO also allows for defining acyclic 
transitive properties using the
class \texttt{acyclicTransitiveRelation}; further, any fact in some YAGO ontology cannot be
described using blank nodes. By carefully checking the rules (\ref{yago:r1}--\ref{yago:r5}) for the reasoning over YAGO ontologies,
one can see that these rules can be rewritten into the datalog rules
of the form (T3),\footnote{Both of Rule (\ref{yago:r1}) and
Rule (\ref{yago:r2}) can be rewritten into (T3).} (T1), (R1) and (R3) in Table~\ref{tab:dhl}, respectively.
{\color{red}I am not sure why in YAGO it is called acyclic transitive
  relation. The rule (in YAGO) is just for transitivity and their
  argument the subclassof is acyclic and transitive does not make much
sense as I can have equivalent classes: C subclassof D, D subclassof
C. That is allowed and cyclic. I would tend to just omit the next
remark. } Further, DHL does not restrict any role to be acyclic.
Based on the above analysis, any YAGO ontology can be expressed in DHL
and satisfies the simple-concept and the simple-role restrictions. We then have that,
for any well-constructed class of YAGO ontologies,
Algorithm~$\mathsf{A}_{opt}^{\psi}$ {\color{red} $\mathsf{A}_{prc}$?
  both is correct, but as we are evaluating $\mathsf{A}_{prc}$ this
  might be better?}
can handle all of the ontologies in the class.

>>>>

\textbf{LUBM}. In the Semantic Web community, LUBM
(The Lehigh University Benchmark) is proposed to
facilitate the evaluation of ontology-based systems
in a standard and systematic way.
In the latest version of LUBM,\footnote{http://swat.cse.lehigh.edu/projects/lubm/}
the core ontology contains 48 classes and 32 properties, used to describe the departments and the staff of
universities. By setting a different number of universities for an ontology-generator, users can get datasets of any size based on the core ontology.
%
The statements about properties in the LUBM core ontology, such as inverse property statements,
can be rewritten into the datalog rules of the form (R1), (R2) and (R3) in Table~\ref{tab:dhl}.
Most of the statements about classes can be rewritten into the datalog rules of the form (T1) and (T3)
in Table~\ref{tab:dhl}. Five axioms have, however, the form $A\sqsubseteq\exists R.B$,
which requires existentially quantified variables in the rule head when rewriting
the axiom into a logic rule: $A(x)\rightarrow\exists y(R(x,y)\wedge B(y))$ ($\tau$),
where a free variable $y$ is introduced. This kind of axiom is a general case of (T4) in Table~\ref{tab:dhl}
for which $A$ is actually replaced by the top concept $\top$.
Similarly to how we handle (T4), we can also eliminate the free variable $y$
in rule $\tau$ via Skolemization, i.e., by replacing the variable $y$ with a new constant $o_R^{A,B}$.
In this way, rule $\tau$ can be rewritten into $A(x)\rightarrow R(x,o_R^{A,B})\wedge B(o_R^{A,B})$.
If we only focus on the materialization task, the rewriting approach via Skolemization guarantees the
completeness and correctness \cite{GrauHKKMMW13}.
On the other hand, rule $\tau$ is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
In summary, if the rewriting approach is used for the above kind of rule,
the materialization of a LUBM dataset can be handled by
Algorithm~$\mathsf{A}_{\text{prc}}$.

@@

According to the semantics given to YAGO \cite{SuchanekKW08}, the built-in properties in YAGO,
i.e., \texttt{domain, range, subClassOf, subRelationOf} and \texttt{type} act in the same
way as the terms in RDFS statements of the form (1--5) in Table~\ref{tab:rdfs}, respectively.
In contrast to RDFS, YAGO also allows for defining
transitive properties using the
class \texttt{acyclicTransitiveRelation}; further, any fact in some YAGO ontology cannot be
described using blank nodes. By carefully checking the rules (\ref{yago:r1}--\ref{yago:r5}) for the reasoning over YAGO ontologies,
one can see that these rules can be rewritten into the datalog rules
of the form (T3),\footnote{Both of Rule (\ref{yago:r1}) and
Rule (\ref{yago:r2}) can be rewritten into (T3).} (T1), (R1) and (R3) in Table~\ref{tab:dhl}, respectively.
Based on the above analysis, any YAGO ontology can be expressed in DHL
and satisfies the simple-concept and the simple-role restrictions. We then have that,
for any well-constructed class of YAGO ontologies,
Algorithm~$\mathsf{A}_{prc}$ 
can handle all of the ontologies in the class.
